The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Changes to documentation.
Updates to Section 3 of paper

The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}.  When
set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.

@@

i11 : fpt(L, m) == o7

@@

In the remainder of this section, we explain how the {\tt fpt} function proceeds when no special algorithm is available, or when {\tt UseSpecialAlgorithms} is set to {\tt false}, and describe the roles of the options {\tt DepthOfSearch} and {\tt Attempts}, whose values are both nonnegative integers.

@@

i11 : f = x^2*(x + y)^3*(x + 3*y^2)^5;

i12 : fpt(f, Attempts => 0) -- a bad estimate

          1
o12 = {0, -}
          5

o12 : List

i13 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate

        21   22
o13 = {---, ---}
       124  125

@@

i14 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand

@@

       22
o14 = ---
      125

o14 : QQ

@@

i15 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;

i16 : fpt(f, Attempts => 1, DepthOfSearch => 3)

       17   7
o16 = {--, --}
       62  25

o16 : List

i17 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint

      nu/(p^e-1) is the F-pure threshold

      17
o17 = --
      62

o17 : QQ

@@

If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval, chosen according to the criteria determined by the value of the option {\tt GuessStrategy}.  We refer the reader for the documentation of this strategy for more details.

{\color{red}  This will need to be updated.  Maybe look at Pedro's new documentation.}

@@

i18 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;

i19 : fpt(f, DepthOfSearch => 3, Attempts => 2)

        3   7
o19 = {--, ---}
       62  125

o19 : List

i20 : fpt(f, DepthOfSearch => 3, Attempts => 3) -- an additional check

      sharpens the estimate

        3   1
o20 = {--, --}
       62  18

@@

i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- and one more finds

      the answer

       1
o21 = --
      19

o21 : QQ
\end{MyVerbatim}
}
\medspace

>>>>

The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}, which, when
set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.

@@

i11 : fpt(L, m) == o8

@@

In the remainder of this section, we explain how the function  {\tt fpt} proceeds when no special algorithm is available, or when {\tt UseSpecialAlgorithms} is set to {\tt false}, and describe the roles of the options {\tt DepthOfSearch} and {\tt Attempts}, whose values are both nonnegative integers.

@@

i12 : f = x^2*(x + y)^3*(x + 3*y^2)^5;

i13 : fpt(f, Attempts => 0) -- a bad estimate

          1
o13 = {0, -}
          5

@@

i14 : fpt(f, Attempts => 0, DepthOfSearch => 3) -- a better estimate

        21   22
o14 = {---, ---}
       124  125

o14 : List

i15 : fpt(f, Attempts => 1, DepthOfSearch => 3) -- the right-hand

@@

       22
o15 = ---
      125

o15 : QQ

@@

i16 : f = x^6*y^4 + x^4*y^9 + (x^2 + y^3)^3;

i17 : fpt(f, Attempts => 1, DepthOfSearch => 3)

       17   7
o17 = {--, --}
       62  25

o17 : List

i18 : fpt(f, Attempts => 2, DepthOfSearch => 3) -- the left-hand endpoint
      nu/(p^e-1) is the F-pure threshold

      17
o18 = --
      62

o18 : QQ

@@

If neither endpoint is the $F$-pure threshold and {\tt Attempts} is set to more than {\tt 2}, then  additional checks are performed at certain numbers within the interval.
First, a number in the interval is selected, according to criteria specified by the value of the option {\tt GuessStrategy}; we refer the reader for the documentation of this option for more details.  
Then the function {\tt compareFPT} is used to test that number. If that "guess" is correct, its value is returned; otherwise, the data returned by {\tt compareFPT} is used to narrow down the interval, and this process is repeated as many times as specified by {\tt Attempts}.

@@

i19 : f = x^3*y^11*(x + y)^8*(x^2 + y^3)^8;

i20 : fpt(f, DepthOfSearch => 3, Attempts => 2)

        3   7
o20 = {--, ---}
       62  125

@@

i21 : fpt(f, DepthOfSearch => 3, Attempts => 4) -- more attempts *always* 
      improve the estimate

        1   4
o21 = {--, --}
       20  75

o21 : List

i22 : fpt(f, DepthOfSearch => 3, Attempts => 4, GuessStrategy => denominator) 
      -- the exact answer, after a change of strategy

       1
o22 = --
      19

o22 : QQ
\end{MyVerbatim}
}
\medspace
